SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Add citations for symbolite backends

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
They can be inspected and compiled to different backends.
Currently, we have implementations for NumPy (and Numba), SymPy and JAX,
but it is easy to add new backends.

>>>>

Symbolite is a lightweight symbolics package to create algebraic mathematical expressions.
They can be inspected and compiled to different backends.
Currently, we have implementations for
NumPy [@harrisArrayProgrammingNumPy2020],
Numba [@lamNumbaLLVMbasedPython2015],
SymPy [@meurerSymPySymbolicComputing2017],
and JAX [@jax2018github],
but it is easy to add new backends.
